\huge A Better (One-Line!) Title Here

### 2016-10-18 pets2017-paper/pets2017-paper.tex
add inspection section, reword titles, mark TODO red.

@@

\subsection{Inspection}
We used a combination of usability inspection methods~\cite{nielsen1994usability}
to prepare for the user study. Two researchers conducted a pluralistic 
walkthrough and stepped through various censorship
scenarios, discussing which elements would be involved for that use case, and walking 
through the configuration process. After compiling all the possible paths through the 
interface, researchers performed feature inspection, listing sequences of features used 
to accomplish typical tasks and taking note of long sequences or cumbersome
steps. In addition, we performed a heuristic evaluation to mark
likely causes of confusion for users during our study.

@@

\section{Redesigning the Configuration Interface}
We make ten changes to the Tor launcher configuration interface to help users connect to Tor. Since users did not know how to connect to Tor, we added advice where our users have previously struggled. Specifically, the following three changes were made to give users more information in during configuration: \\

\label{redesign}

@@

These changes result in a redesigned interface which we refer to as NEW. Note that the new interface preserves all the functionality of the old interface and still allows users to have control over their own network traffic.

\section{Evaluation Criteria}
\label{sec:eval}
Our user studies evaluated two versions of the Tor Launcher interface.
The first, which we have labeled OLD in our figures and tables,
is the current version being distributed with Tor Browser.
The second, NEW, is the prototype that we designed
in order to provide better usability. Below are the empirical and 
heuristic evaluation criteria we use to assess the interfaces.

@@

An ideal interface maximizes the amount of people that successfully connect to the Tor network, while minimizing the time it takes to connect to the Tor network. A trade-off may be required between the total amount of time it takes to connect to Tor and the amount of time users interact with the interface. For instance, a  process with a balanced amount of user input may be faster than a naive but completely automated process.

\section{Quantitative Analyses of the Interfaces (Study 2)}
\label{sec:quantitative}
Having identified problems with the existing interface
and made changes to ameliorate them,
we quantify the existing problems
and the impact of our changes with a study involving a larger number of users.
We split participants by simulated censorship environments,
and between old and new interfaces.

@@

We performed a one-tailed Mann--Whitney test to compare the amount of active configuration time between participants who used the new interface and the participants who used the old interface. Our changes to the interface reduced the time participants spent configuring the interface (Mann--Whitney $Z = -3.28$, $p = 0.000516$, $r = 0.307$).  Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.

\section{Discussion} 
\label{sec:discussion}
We talk about the failure cases and behavioral trends observed in our quantitative user study and recommend some changes to the Tor configuration interface based on those observations.

@@

\subsubsection{Recommendations}
\label{recommendations}
Based on our observations of general behavioral trends and common failure cases, we make the following recommendations to increase success rate and decrease overall time spent in the interface: \\

@@

Although we cannot isolate their effects on users, we also recommend notifying a users with the configured settings before connecting and having a progress bar that illustrates when network component have successfully been configured or failed.

\section{Limitations}
\label{sec:limitations}
The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems. We only tested interface on Windows machines, which were the machines available at <redacted>. %Xlab. 
Participants who are not accustomed to Windows machines may have been slower to complete the given task, but this affected all conditions equally.

@@

\section{Related Work}
\label{sec:related} 
There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and FoxyProxy, and found that none had satisfactory from a usability. Fabian et~al.~\cite{fabian2010privately} show that Tor's added
latency~\cite{dingledine2009performance} causes users
to be frustrated, cancel requests, and prevents user adoption. 
Norcie et~al.~\cite{norcie2012eliminating} found found that 
64\% of users are unable to continue with installation or browsing at least once due to difficulties.

@@

Previous user studies have considered the whole browsing experience,
without focusing on specific features in isolation.
Our study focuses on 
the browser's configuration interface, which guides users through setting up components required to circumvent censorship.

\section{Conclusion} 
\label{sec:conclusion}
We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface, focusing on users who use Tor to circumvent censorship. Since connecting to the Tor network unsuccessfully indicates to network eavesdroppers that users are connecting to Tor, the configuration process is manual to allow users to have control over the network activity. Through interviews and lab studies, we find that users have difficulty configuring network components to circumvent censorship, because they do not know how censorship or Tor works. We detail the common challenges, our changes to the configuration interface address those challenges, and the recommendations we have for Tor in this paper.

@@

@@

\appendix
\section{Alternative Approaches} 
%In principle, the process of configuring a proxy and bridge can be automated, but
%the interface eschews automatic configuration through network probing
%in favor of guided manual configuration to give users agency in configuring their connection. 
%Automatic configuration through network probing may put some users in certain regimes at risk. 
%A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
%However, this requires that the user grapple with technical concepts such as 
%bridges, pluggable transports, and proxies. Some of these concepts are specific to 
%Tor and not general concepts.

@@

We believe that automation, asking about risk, and identifying struggling users could enable significant improvements to the configuration process.

@@

\section{Statistical Tests} 
\label{stat-tests}
From our measurements, we observe that participants with the new interface 
have a higher rate of success, succeed in less time, and configure their interface in less time. 
We do not find that the increased rate of success with the new interface or the decreased time to success with the new interface significant. That is, random chance can account for the difference. 
We do find the the decreased active configuration time to be significant. 
We describe the methodology for the statistical tests used in this paper to determine the impact of the interface on success rate, time to success, and active time.

@@

%active time and version
Active configuration time was measured as the time the participants spent in the Tor launcher interface, except for the time spent the progress screen. For our participants who did not succeed to connect to Tor, subtracted the time spent on the progress screen from the maximum experiment time of 40 minutes. This measurement was also 1) non-normal and heavily right tailed and 2) impacted by right-censored measurement of time to success. Because of the right-tailed nature of the data, we used a one-tailed Mann--Whitney test. We find the difference of active configuration times between participants with the new interface and participants with the old interface to be significant ($Z = -3.28$, $p = 0.000516$, $r = 0.307$).

>>>>

%%%%%% LINDA'S PASS UP TO HERE %%%%%%%%%
\section{Usability Inspection}
{\color {red}
We used a combination of usability inspection methods~\cite{nielsen1994usability}
to prepare for the user study. Two researchers conducted a pluralistic 
walkthrough and stepped through various censorship
scenarios, discussing which elements would be involved for that use case, and walking 
through the configuration process. After compiling all the possible paths through the 
interface, researchers performed feature inspection, listing sequences of features used 
to accomplish typical tasks and taking note of long sequences or cumbersome
steps. In addition, we performed a heuristic evaluation to mark
likely causes of confusion for users during our study.
}

@@

@@

%for color red
}

\section{Design Principles and Changes}
\label{redesign} 
{\color {red}
We make ten changes to the Tor launcher configuration interface to help users connect to Tor. Since users did not know how to connect to Tor, we added advice where our users have previously struggled. Specifically, the following three changes were made to give users more information in during configuration: \\

@@

These changes result in a redesigned interface which we refer to as NEW. Note that the new interface preserves all the functionality of the old interface and still allows users to have control over their own network traffic. 
%for color red
}

\section{Evaluation Method and Criteria}
\label{sec:eval}
{\color {red} 
Our user studies evaluated two versions of the Tor Launcher interface.
The first, which we have labeled OLD in our figures and tables,
is the current version being distributed with Tor Browser.
The second, NEW, is the prototype that we designed
in order to provide better usability. Below are the empirical and 
heuristic evaluation criteria we use to assess the interfaces.

@@

An ideal interface maximizes the amount of people that successfully connect to the Tor network, while minimizing the time it takes to connect to the Tor network. A trade-off may be required between the total amount of time it takes to connect to Tor and the amount of time users interact with the interface. For instance, a  process with a balanced amount of user input may be faster than a naive but completely automated process.
%for color red
}

\section{Quantitative User Testing}
\label{sec:quantitative}

{\color {red} 
Having identified problems with the existing interface
and made changes to ameliorate them,
we quantify the existing problems
and the impact of our changes with a study involving a larger number of users.
We split participants by simulated censorship environments,
and between old and new interfaces.

@@

We performed a one-tailed Mann--Whitney test to compare the amount of active configuration time between participants who used the new interface and the participants who used the old interface. Our changes to the interface reduced the time participants spent configuring the interface (Mann--Whitney $Z = -3.28$, $p = 0.000516$, $r = 0.307$).  Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.
%for color red
}

\section{Discussion} 
\label{sec:discussion}

{\color {red} 
We talk about the failure cases and behavioral trends observed in our quantitative user study and recommend some changes to the Tor configuration interface based on those observations.

@@

%for color red
}

\subsubsection{Recommendations}
\label{recommendations}
{\color {red} 
Based on our observations of general behavioral trends and common failure cases, we make the following recommendations to increase success rate and decrease overall time spent in the interface: \\

@@

Although we cannot isolate their effects on users, we also recommend notifying a users with the configured settings before connecting and having a progress bar that illustrates when network component have successfully been configured or failed.
%for color red
}

\section{Limitations}
\label{sec:limitations}
{\color {red} 
The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems. We only tested interface on Windows machines, which were the machines available at <redacted>. %Xlab. 
Participants who are not accustomed to Windows machines may have been slower to complete the given task, but this affected all conditions equally.

@@

%for color red
}

\section{Related Work}
\label{sec:related}

{\color {red} 
There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and FoxyProxy, and found that none had satisfactory from a usability. Fabian et~al.~\cite{fabian2010privately} show that Tor's added
latency~\cite{dingledine2009performance} causes users
to be frustrated, cancel requests, and prevents user adoption. 
Norcie et~al.~\cite{norcie2012eliminating} found found that 
64\% of users are unable to continue with installation or browsing at least once due to difficulties.

@@

Previous user studies have considered the whole browsing experience,
without focusing on specific features in isolation.
Our study focuses on 
the browser's configuration interface, which guides users through setting up components required to circumvent censorship. 
%for color red
}

\section{Conclusion} 
\label{sec:conclusion}

{\color {red} 
We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface, focusing on users who use Tor to circumvent censorship. Since connecting to the Tor network unsuccessfully indicates to network eavesdroppers that users are connecting to Tor, the configuration process is manual to allow users to have control over the network activity. Through interviews and lab studies, we find that users have difficulty configuring network components to circumvent censorship, because they do not know how censorship or Tor works. We detail the common challenges, our changes to the configuration interface address those challenges, and the recommendations we have for Tor in this paper.

@@

%for color red
}

@@

\appendix
\section{Alternative Approaches} 
{\color {red} 
%In principle, the process of configuring a proxy and bridge can be automated, but
%the interface eschews automatic configuration through network probing
%in favor of guided manual configuration to give users agency in configuring their connection. 
%Automatic configuration through network probing may put some users in certain regimes at risk. 
%A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
%However, this requires that the user grapple with technical concepts such as 
%bridges, pluggable transports, and proxies. Some of these concepts are specific to 
%Tor and not general concepts.

@@

We believe that automation, asking about risk, and identifying struggling users could enable significant improvements to the configuration process. 
%for color red
}

@@

\section{Statistical Tests} 
\label{stat-tests}
{\color {red} 
From our measurements, we observe that participants with the new interface 
have a higher rate of success, succeed in less time, and configure their interface in less time. 
We do not find that the increased rate of success with the new interface or the decreased time to success with the new interface significant. That is, random chance can account for the difference. 
We do find the the decreased active configuration time to be significant. 
We describe the methodology for the statistical tests used in this paper to determine the impact of the interface on success rate, time to success, and active time.

@@

%active time and version
Active configuration time was measured as the time the participants spent in the Tor launcher interface, except for the time spent the progress screen. For our participants who did not succeed to connect to Tor, subtracted the time spent on the progress screen from the maximum experiment time of 40 minutes. This measurement was also 1) non-normal and heavily right tailed and 2) impacted by right-censored measurement of time to success. Because of the right-tailed nature of the data, we used a one-tailed Mann--Whitney test. We find the difference of active configuration times between participants with the new interface and participants with the old interface to be significant ($Z = -3.28$, $p = 0.000516$, $r = 0.307$).
%for color red
}
